Figures and Tables

### 2021-03-04 paper/figures_tables.Rmd
Save figures as separate files

ggplot() +
  geom_path(data = animalTraj, aes(x = xloc, y = yloc), size = 1, color = "darkgrey") +
  geom_point(data = animalTraj, aes(x = xloc, y = yloc), color = "black") +
  geom_point(data = seed_loc, aes(x = xloc, y = yloc), color = "red", size = 3) +
  geom_point(aes(x = 0, y = 0), color = "black", size = 5)+
  geom_vline(aes(xintercept=0), linetype = "dotted") + geom_hline(aes(yintercept = 0), linetype = "dotted") +
  labs(x = "x", y = "y") +
  coord_fixed() +
  theme_bw() -> fig_traj

@@

```{r fig.width=2.5, fig.height=4}
plot_grid(fig_GRT, fig_MD, align = "v", nrow = 2, labels = "AUTO", label_size = 10)

# ggsave("paper/figures/Figure1.png",
#        width = 2.5,
#        height = 4,
#        units = "in",
#        dpi = 300)
```

@@

```{r fig.height=2, fig.width=6}
plot_grid(fig_traj, fig_disp, fig_agg, ncol = 3, align = "h", labels = "AUTO", label_size = 8)

# ggsave("paper/figures/Figure2.png",
#        width = 6,
#        height = 2,
#        units = "in",
#        dpi = 300)
```

@@

plot_grid(weib_dens, gp_dens, ncol = 2, labels = "AUTO", label_size = 8)

# ggsave("paper/figures/Figure3.png",
#        width = 6,
#        height = 2.5,
#        units = "in",
#        dpi = 300)

@@

boxplots <- plot_grid(a,b, ncol = 2, align = "h", labels = c("B", "C"))

plot_grid(dens_by_id, boxplots, nrow=2, labels = c("A", ""))

# Edit redundant labels
# Fix names for axes

>>>>

ggplot() +
  geom_path(data = animalTraj, aes(x = xloc, y = yloc), 
            #size = 1,
            color = "darkgrey") +
  geom_point(data = animalTraj, aes(x = xloc, y = yloc), color = "black") +
  geom_point(data = seed_loc, aes(x = xloc, y = yloc), color = "red", size = 3) +
  geom_point(aes(x = 0, y = 0), color = "black", size = 5)+
  geom_vline(aes(xintercept=0), linetype = "dotted") + geom_hline(aes(yintercept = 0), linetype = "dotted") +
  labs(x = "x", y = "y") +
  coord_fixed() +
  theme_bw() -> fig_traj

@@

```{r fig.width=2.5, fig.height=4}
plot_grid(fig_GRT, fig_MD, align = "v", nrow = 2, labels = "auto", label_size = 10)

# ggsave(filename = "figures/Figure1.tiff",
#        device = "tiff",
#        width = 2.5,
#        height = 4,
#        units = "in",
#        dpi = 300)
```

@@

```{r fig.height=2, fig.width=6}
plot_grid(fig_traj, fig_disp, fig_agg, ncol = 3, align = "h", labels = "auto", label_size = 8)

# ggsave("figures/Figure2.tiff",
#        width = 6,
#        height = 2,
#        units = "in",
#        dpi = 300)
```

@@

plot_grid(weib_dens, gp_dens, ncol = 2, labels = "auto", label_size = 8)

# ggsave("figures/Figure3.tiff",
#        width = 6,
#        height = 2.5,
#        units = "in",
#        dpi = 300)

@@

boxplots <- plot_grid(a,b, ncol = 2, align = "h", labels = c("b", "c"))

plot_grid(dens_by_id, boxplots, nrow=2, labels = c("a", ""))

# ggsave(filename = "figures/Figure4.tiff",
#        device = "tiff",
#        width = 6,
#        height = 6,
#        units = "in",
#        dpi = 300)
